Data Exploration: IUCN and AquaMaps

### 2017-04-10 data_explore/data_explore.Rmd
changing the coral quadplot to mini plot
using tmap for maps; figured out the headspace problem using aspect ratio and inner/outer margin.

### define 25%, 50%, and 75% quartiles for both x and y axes
area_align_mean <- mean(spp_list$area_ratio, na.rm = TRUE)
dist_align_mean <- mean(spp_list$sm_perc, na.rm = TRUE)

>>>>

### define means for both x and y axes
area_align_mean <- mean(spp_list$area_ratio, na.rm = TRUE)
dist_align_mean <- mean(spp_list$sm_perc, na.rm = TRUE)
